\LARGE Micro- versus meso-scale population models for ecological forecasting under climate change

### 2014-10-26 manuscript/ms_MicroMeso.Rnw
ms formatting updates

\documentclass[12pt]{article}
\usepackage{graphics}
\usepackage{graphicx, verbatim}
\usepackage{amssymb,amsmath}
\usepackage{tabularx}
% \usepackage[T1]{fontenc}
% \usepackage[utf8]{inputenc}
\usepackage{authblk}
\textwidth=6.2in
\textheight=8.5in
%\parskip=.3cm
\oddsidemargin=.1in
\evensidemargin=.1in
\headheight=-.3in

@@

\title{\LARGE Micro- versus meso-scale population models for ecological forecasting under climate change}
\author[]{\large Andrew T. Tredennick} 
\author[]{\large Peter B. Adler}
\affil[]{\footnotesize{\emph{Department of Wildland Resources and the Ecology Center, Utah State University}}}
\maketitle

@@

Add section on recruitment...

@@

We used the analytical Bayesian software INLA to fit the candidate models and selected the model with the lowest Deviance Information Criteria (DIC). However, for many species there were several models with $\Delta$DIC < 4, indicating that each model received generally the same amount of support. So, among the models with $\Delta$DIC < 4, we chose the model with the fewest number of parameters. In some cases this resulted in selecting a model with no climate covariates.

@@

>>>>

\documentclass[12pt]{article}
\usepackage{graphics}
\usepackage{graphicx, verbatim}
\usepackage{amssymb,amsmath}
\usepackage{tabularx}
% \usepackage[T1]{fontenc}
% \usepackage[utf8]{inputenc}
\usepackage{authblk}
\textwidth=6.2in
\textheight=8.5in
%\parskip=.3cm
\oddsidemargin=.1in
\evensidemargin=.1in
\headheight=-.3in
\usepackage{lineno}
\linenumbers
\modulolinenumbers[2]
\usepackage{setspace}
\doublespacing

@@

\title{\LARGE Micro- versus meso-scale population models for ecological forecasting under climate change}
\author[]{\large Andrew T. Tredennick\footnote{\emph{email:} atredenn@gmail.com}}
\author[]{\large Peter B. Adler}
\affil[]{\footnotesize{\emph{Department of Wildland Resources and the Ecology Center, Utah State University}}}
\maketitle

@@

While our approach for modeling survival and growth is similar at the individual and quadrat levels, the addition of new genets at the inidividual level or occupied sites at the quadrat level requires two separate approaches.

@@

We based model selection on the Deviance Information Criteria (DIC). However, for many species there were several models with $\Delta$DIC < 4, indicating that each model received generally the same amount of support. Given this ambiguity, we opted to simply select the candidate model with lowest DIC, regardless of the statistical nearness of other models, as the final model to use for simulating the population dynamics. In some cases this resulted in selecting a model with no climate covariates. We had to choose a single statistical model for each vital rate for our population models, but when comparing climate covariate selection between the individual and quadrat levels we acknowledge climate covariates selected in all models with $\Delta$DIC < 4.

\subsection{Computing}
\subsubsection{Model fitting}
All of our analyses (model selection, fitting, and simulating) were conducted in R. We used the analytical Bayesian software INLA to fit candidate vital rate models at the individual and quadrat levels for computational efficiency. This is the case except for the recruitment model at the individual level which required a more complex hierarchical approach. In that case we used the MCMC sampler in JAGS to estimate the posterior distributions of model parameters. After model selection, we used MCMC samplers, again in JAGS, to estimate the posterior distributions of model parameters for all vital rate models at the individual and quadrat levels. We obtained posterior distributions for all model parameters from three MCMC chains run for 10,000 iterations, after discarding the initial 5,000 iterations. We assessed convergence visually and using the Gelman diagnostic in the R package `coda.'

\subsubsection{Population models}
With the posterior distribution of the vital rate statistical models in hand, it is straightforward to simulate the population models.

@@

% # <<echo=FALSE, fig=TRUE,height=3,width=8.5 >>=
% # library(ggplot2)
% # plotD <- data.frame(Species = rep(growthSSRTable$Species, 3),
% #                     Model = rep(c("Growth", "Survival", "Colonization"), each=4),
% #                     Contribution = c(growthSSRTable[,6],
% #                                      survivalSSRTable[,6],
% #                                      colonizationSSRTable[,6]))
% # ggplot(plotD, aes(x=Species, y=Contribution))+
% #   geom_bar(stat="identity")+
% #   facet_grid(.~Model)
% # @
